---
title: "Assessment1-part1"
author: "Ryosuke Otsuka s4663911"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Assessment 1 part 1"
author: "Ryosuke Otsuka s4663911"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Setup your Assessment 1 project:

2 Create the heading of the first level and call it RMarkdown editing 

# RMarkdown editing

3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)


**R Markdown** allows you to create documents that *serve as a neat record of your analysis*. In the world of reproducible research, *we want other researchers to easily understand what we did in our analysis*, **otherwise nobody can be certain that you analysed your data properly**.

4. In the above use bold and italics for editing. 

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html 

[here]("https://rmarkdown.rstudio.com/lesson-8.html")


6. Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv
```{r}
#library(tidyverse)
```


```{r}

fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```


7. Display the first 10 rows of the dataset using head() and kable(). 
Display the first 10 rows of the dataset and the first 5 variables

```{r}
#library(knitr)
```

```{r}
head(fastfood, 10)
```
```{r}
head(fastfood[1:10,1:5])
```

```{r}
knitr::kable(head(fastfood[1:10,]), "pipe")

```

```{r}
knitr::kable(head(fastfood[1:10, 1:5]), "pipe")

```


